\subsection{Adopted frameworks}
The development of the application has been facilitated by the adoption of notable frameworks.
\begin{itemize}
    \item \textbf{Spring Boot}: we used Spring Boot as the backend framework, simplifying the development of the application. It provides the embedded server and auto-configuration required to run the Java-based system.
    \item \textbf{Vue.js}: for the frontend, we decided to use Vue.js, which enabled fast development of an interactive UI.
    \item \textbf{JUnit and Mockito}: for testing the backend we used JUnit and Mockito to perform unit testing with mocked dependencies.
\end{itemize}

\subsection{Adopted programming languages}

\paragraph{Java}
The backend has been completely written in Java, which has been used to define the entities, the business logic services, and the REST controllers that expose the API to the client.

\paragraph{Java Pros}
\begin{itemize}
    \item \textbf{Statically Typed}: being strongly typed ensures that type errors are caught at compile-time rather than runtime, making the system more robust.
    \item \textbf{Rich Ecosystem}: the availability of libraries like JTS for geospatial operations sped up development.
    \item \textbf{Multithreading}: Java's native support for multithreading allows the application to handle concurrent tasks, such as fetching weather data asynchronously.
\end{itemize}

\paragraph{Java Cons}
\begin{itemize}
    \item \textbf{Memory Consumption}: the Java Virtual Machine tends to consume more memory compared to lighter runtime environments.
\end{itemize}

\paragraph{TypeScript}
The frontend has been written in TypeScript. 

\paragraph{TypeScript Pros}
\begin{itemize}
    \item \textbf{Type Safety}: it brings the advantages of static typing to JavaScript.
    \item \textbf{Maintainability}: in complex frontend projects, explicit interfaces and types make the code easier to read and maintain.
\end{itemize}

\paragraph{Other languages}
Additionally, HTML  and CSS  were used to define the structure and styling of the pages.

\subsection{Adopted middlewares and libraries}

\subsubsection*{Backend}
\paragraph{Middlewares}
\begin{itemize}
    \item \textbf{Spring Security}: used for managing authentication and authorization.
    \item \textbf{Spring Data JPA}: used for database abstraction, allowing data manipulation via Repository interfaces.
\end{itemize}

\paragraph{Libraries}
\begin{itemize}
    \item \textbf{JJWT}: used for JWT token creation and validation.
    \item \textbf{MapStruct}: used for compile-time Entity-DTO mapping.
    \item \textbf{Lombok}: used to reduce boilerplate code.
    \item \textbf{JTS (Java Topology Suite)}: used for geospatial operations and geometric calculations.
    \item \textbf{Resilience4j}: used for rate limiting requests to external APIs.
    \item \textbf{Caffeine}: used as high-performance caching library for external API responses.
    \item \textbf{H2 Database}: used as in-memory database for development and testing.
\end{itemize}

\subsubsection*{Frontend}
\paragraph{Libraries}
\begin{itemize}
    \item \textbf{Pinia}: used as the state manager.
    \item \textbf{Vue Router}: used for client-side navigation, mapping URLs to Vue components.
    \item \textbf{Axios}: used to perform asynchronous HTTP requests to the backend.
    \item \textbf{Mapbox GL}: used for interactive map rendering and visualization.
    \item \textbf{Tailwind CSS}: used to rapidly style components, ensuring visual consistency.
    \item \textbf{DaisyUI}: used as UI component library built on Tailwind CSS.
    \item \textbf{Lucide Vue Next}: used for icons.
\end{itemize}

\subsection{Adopted APIs}
The system relies on the following external APIs:
\begin{itemize}
    \item \textbf{Mapbox}: used for geocoding (address to coordinates conversion and reverse), and cycling route calculation.
    \item \textbf{Open-Meteo}: used to retrieve historical weather data for trip enrichment.
\end{itemize}