\subsection{Test Cases}
Unit tests were developed using the JUnit framework and Mockito to isolate business logic and simulate external dependencies .

\subsubsection{User Management Services}
Testing for user management covers both authentication and profile modification. The following tests were executed:

\begin{itemize}
    \item \textbf{Authentication}:
    \begin{itemize}
        \item Registration with valid information.
        \item Registration with an existing username.
        \item Registration with an email already in use.
        \item Login with valid credentials.
        \item Login with non-existent email.
        \item Login with incorrect password.
    \end{itemize}
    
    \item \textbf{Profile Management}:
    \begin{itemize}
        \item Full user profile update.
        \item Partial update.
        \item Update with a username already taken by another user.
        \item Update with an email already taken by another user.
        \item Update without any variation.
        \item Deletion of the current user account.
    \end{itemize}
\end{itemize}

\noindent All tests passed successfully, ensuring sensitive data security and credential uniqueness.

\subsubsection{Bike Path Operations}
Tests related to bike paths verify the complete lifecycle of a path, from manual creation to search, including privacy management. The following tests were executed:

\begin{itemize}
    \item \textbf{CRUD Operations}:
    \begin{itemize}
        \item Manual creation of a path.
        \item Retrieval of a public path.
        \item Retrieval of a private path by the creator.
        \item Attempted retrieval of a private path by a third party.
        \item Retrieval of a non-existent path.
        \item Update of path metadata by the owner.
        \item Concurrent update with an obsolete version.
        \item Deletion of a path by the owner.
    \end{itemize}
    
    \item \textbf{Search}:
    \begin{itemize}
        \item Path search with filters and data enrichment.
        \item Geographic search within a specific radius between origin and destination.
        \item Result filtering based on real distance.
        \item Pagination handling with valid and non-valid parameters.
    \end{itemize}
\end{itemize}

\noindent All tests passed, confirming the correct application bike path's logic.

\subsubsection{Trip Service}
This section tests the recording and management of personal trips, verifying integration with weather services. The following tests were executed:

\begin{itemize}
    \item \textbf{Trip Recording}:
    \begin{itemize}
        \item Manual recording of a trip with valid data.
        \item Trip recording even in case of external weather service failure.
    \end{itemize}
    
    \item \textbf{Trip Management}:
    \begin{itemize}
        \item View trip details by the owner.
        \item Attempt to view another user's trip.
        \item Deletion of an existing trip.
        \item Search and pagination of the user's trip history.
    \end{itemize}
\end{itemize}

\noindent All tests passed.

\subsubsection{Obstacle Management}
Tests verify the spatial logic for placing obstacles along the path and calculating the safety score. The following tests were executed:

\begin{itemize}
    \item \textbf{Obstacle Lifecycle}:
    \begin{itemize}
        \item Creation and saving of obstacles within the path buffer.
        \item Rejection of obstacle creation if placed too far from the path.
        \item Update of an existing obstacle.
        \item Addition of new obstacles during an update phase.
    \end{itemize}
    
    \item \textbf{Scoring}:
    \begin{itemize}
        \item Score calculation with an empty obstacle list.
        \item Penalty calculation based on severity and active/inactive status of obstacles.
    \end{itemize}
\end{itemize}

\noindent All tests passed.

\subsubsection{External Integrations (Mapbox and Open-Meteo)}
The following tests are performed to ensure system resilience against failures from third-party APIs. The following tests were executed:

\begin{itemize}
    \item \textbf{Mapbox Service}:
    \begin{itemize}
        \item Geocoding of valid addresses.
        \item Handling of invalid or not found addresses.
        \item Handling of network errors.
        \item Handling of API limits.
        \item Bike route calculation with multiple waypoints.
    \end{itemize}
    
    \item \textbf{OpenMeteo Service}:
    \begin{itemize}
        \item Retrieval of correct historical weather data.
        \item Handling of requests with dates that are too old.
        \item Handling of timeouts and server errors.
        \item Handling of empty or malformed responses.
    \end{itemize}
\end{itemize}

\noindent All tests passed.