\subsection{Purpose}
Best Bike Paths is a software system that enables cyclists to create and browse through an inventory of bike paths.

\noindent For \textbf{registered users} it serves as a personal cycling log to track their trips and as a tool to contribute bike path information to the community. The application provides useful data about each trip, such as the total covered distance, average speed, and other performance metrics. When available, it can enrich trip records with meteorological information (such as weather conditions, temperature, humidity, and wind speed).
Registered cyclists can also report details about bike paths, including the quality status of the roads and the presence of obstacles.

\noindent Both trips and bike paths can be added to the software in two ways:
\begin{itemize}
    \item[] \textbf{Manual mode}: this mode allows users to manually insert the streets composing their route and report the location of any obstacles encountered, through the web app or smartphone app.
    \item[] \textbf{Automated mode}: this mode allows the smartphone app to start recording when it detects that the user is cycling. Through GPS, the software will map the route taken, while the accelerometer and gyroscope detect potential obstacles. After user validation, the recorded data will be saved in the system. 
\end{itemize}
\noindent Details about bike paths can be made publishable by the owner, making them visible and accessible to the entire community.
Every user, registered or not, can access the system to search for bike paths between a starting location and a destination. BBP visualizes available paths on a map and ranks them based on a quality score computed from the path status and the presence of obstacles.

\subsubsection{Goals}
\begin{itemize}
    \item[] \textbf{[G1] Planning best and most efficient bike path:} 
    Allow every user (registered or not) to find bicycle paths from an origin to a destination, ranked by a quality score computed from the path status and the presence of obstacles.

    \item[] \textbf{[G2] Storing the cycling activity of registered users:} 
    Give registered users a tool to track their cycling sessions, enriching trip data with performance metrics (distance, speed, duration) and, when available, meteorological information.

    \item[] \textbf{[G3] Automatic cycling activity recognizer and recorder:} 
    Automatically record the cycling route via GPS and detect potential obstacles based on the user's phone sensors (accelerometer and gyroscope).

    \item[] \textbf{[G4] Automatically detect cycling stop and verify gathered data:} 
    Prompt the user with a confirmation message to accept the ended activity, with the possibility to confirm or correct detected obstacles before they are recorded.

    \item[] \textbf{[G5] Permitting manual insertions:} 
    Give registered users the possibility to manually insert trips and bike paths, specifying streets, timings, status, and obstacles.

    \item[] \textbf{[G6] Publication control:} 
    Allow users to control bike path visibility by making them publishable to the community or keeping them private.
\end{itemize}

\subsection{Scope}
This section defines the scope of the Best Bike Paths (BBP) system using the \textit{World and the Machine} approach. This framework distinguishes between two domains: the \textbf{World}, which comprises phenomena that occur in the application domain, and the \textbf{Machine}, which is the software system itself. The intersection between these two domains defines the \textbf{Shared Phenomena}: a set of phenomena that occur in the World and are monitored by the Machine, or are controlled by the Machine and observed by the World.

\subsubsection*{The World Phenomena}
\begin{itemize}
\item[] \textbf{WP1:} Users cycle in the physical world on different types of roads.
\item[] \textbf{WP2:} The physical world has various conditions, such as road quality, obstacles, weather.
\item[] \textbf{WP3:} Users want to find a bike path from an origin to a destination.
\item[] \textbf{WP4:} Users want to open the app to record their track.
\item[] \textbf{WP5:} Users evaluate the results that the app gives them after they finished cycling.
\item[] \textbf{WP6:} Users decide to publish their bike paths or not to.
\item[] \textbf{WP7:} External service providers update their data independently from BBP.
\end{itemize}

\subsubsection*{The Machine}
The BBP system is the software component to be developed.

\subsubsection*{Shared Phenomena}

\begin{itemize}
\item[] \textbf{SP1:} Users send their registration data (email and password) to the system.
\item[] \textbf{SP2:} Users send their login credentials to the system or press the logout button.
\item[] \textbf{SP3:} BBP app acquires sensor data (gyroscope, accelerometer) from the user's phone.
\item[] \textbf{SP4:} Users manually insert trip details (origin, destination, timings) through the user interface.
\item[] \textbf{SP5:} Users manually insert bike path details (streets, status, obstacles) through the user interface.
\item[] \textbf{SP6:} Users send the search parameters (the origin and the destination) to the system.
\item[] \textbf{SP7:} The system sends requests to external service providers to get weather data or map data.
\item[] \textbf{SP8:} External service providers send weather data and map data to the system.
\item[] \textbf{SP9:} The system shows to users maps and paths.
\item[] \textbf{SP10:} The system proposes detected obstacles to the user for validation.
\item[] \textbf{SP11:} Users send a confirmation or correction of the detected obstacles.
\item[] \textbf{SP12:} Users request their trip history and the system displays trip information such as average speed, distance, and weather conditions.
\item[] \textbf{SP13:} Users send a confirmation for the publication of the bike path or send a confirmation to keep the bike path private.
\item[] \textbf{SP14:} Users request to update their bike paths (status and published flag) or delete them, and the system processes the modification.
\item[] \textbf{SP15:} Users add or update obstacles on bike paths (type, severity, active status) through the user interface.
\item[] \textbf{SP16:} Users request to delete their trips, and the system processes the deletion.
\item[] \textbf{SP17:} Users request to update or delete their account, and the system processes the modification.
\item[] \textbf{SP18:} Users report new obstacles on existing public bike paths through the user interface.
\end{itemize}

\subsection{Definitions, Acronyms, and Abbreviations}
\begin{table}[H]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|p{3.5cm}|p{10cm}|}
\hline
\textbf{Term / Acronym} & \textbf{Definition} \\
\hline
\textbf{API} & Application Programming Interface \\
\hline
\textbf{BBP} & Best Bike Paths \\
\hline
\textbf{CRUD} & Create, Read, Update, Delete \\
\hline
\textbf{DD} & Design Document \\
\hline
\textbf{DTO} & Data Transfer Object \\
\hline
\textbf{GDPR} & General Data Protection Regulation \\
\hline
\textbf{GPS} & Global Positioning System \\
\hline
\textbf{HTTPS} & Hypertext Transfer Protocol Secure \\
\hline
\textbf{JSON} & JavaScript Object Notation \\
\hline
\textbf{JWT} & JSON Web Token \\
\hline
\textbf{Quality Score} & Path quality score calculated based on number of obstacles and time taken for going from one place to another \\
\hline
\textbf{RASD} & Requirement Analysis and Specification Document \\
\hline
\textbf{REST} & Representational State Transfer \\
\hline
\textbf{SDK} & Software Development Kit \\
\hline
\textbf{LLM} & Large Language Model \\
\hline
\textbf{AI} & Artificial Intelligence \\
\hline
\end{tabular}
\caption{Definitions, Acronyms, and Abbreviations}
\label{tab:definitions}
\end{table}

\subsection{Revision History}
\begin{table}[h!]
\centering
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Version} & \textbf{Date} & \textbf{Authors} \\
\hline
1.0 & 22-12-2025 & Raimondi F., Sala M. \\
\hline
\end{tabular}
\caption{Document Revision History}
\end{table}

\subsection{Reference Documents}
\begin{enumerate}
    \item A.Y. 2025-2026 Software Engineering 2 - Project Specification \cite{project_spec}.
\end{enumerate}

\subsection{Document Structure}
This document is organized into six main sections, following the standard structure for Requirement Analysis and Specification Documents:

\begin{itemize}
    \item[] \textbf{Introduction:} This section offers a general view of the BBP project, here the purpose and scope are defined.
    \item[] \textbf{Overall Description:} This section describes the context in which the system operates. Here the system is described with the \textit{World and Machine} approach. Perspectives, user characteristics, assumptions and constraints are detailed.
    \item[] \textbf{Specific Requirements:} This section details the external interface requirements, functional requirements, and non-functional requirements.
    \item[] \textbf{Formal Analysis using Alloy:} This section provides a formal model of the critical aspects of the system to validate the consistency and correctness of the specifications.
    \item[] \textbf{Use of Generative AI Tools:} This section describes the AI tools employed during document preparation, including writing assistance and UI mockup generation, along with verification processes.
    \item[] \textbf{Effort Spent:} This section shows the number of hours spent by each group member.
    \item[] \textbf{References:} This section lists the resources used as references in this document.
\end{itemize}