\subsection{Product Perspective}
BBP's system act as an intermediary between the cyclist and the digital inventary of paths. 
It works as a distributed system made of a mobile app (for live tracking and sensors data acquisition) and a web app (for path visualization, for managing user's paths and for manual path insertions) both web app and mobile app communicate with a central backend.
The system interact with external entities such a weather's APIs to get weather data and map's APIs to visualize and geolocate paths.

\subsubsection{Scenarios}
The following scenarios shows the typical interaction with the system, highlighting how BBP reach its main goals and real scenarios.

\paragraph{Scenario 1: Automatic tracking and Data Acquisition Through Sensors}
\textbf{Actors:} Alice (Registered User), Mobile App, Phone's gyroscope and accelerometer.\\
Alice with BBP's mobile app installed on her phone starts cycling.
\begin{enumerate}
    \item When Alice reaches a speed typical of cycling (between 15 km/h and 20 km/h), BBP's app detects an activity.
    \item The system starts recording Alice's path by saving GPS coordinates every 500ms.
    \item While cycling Alice hits a pothole, BBP's app will then register the data acquired through the gyroscope and recognize the presence of a pothole.
    \item The system will record the GPS coordinates of the pothole as possible pothole.
    \item Arrived at destination, Alice stops. BBP's app will recognize a prolonged stop and will stop recording the path, marking it as complete.
    \item The system will create an hypotetical evalutaion of the entire track based on Alice's short stops, and the gyroscope variations.
    \item BBP will show a summary of the path and will ask Alice to validate the aquired data (time, path and obstacles, in this scenario the pothole).
    \item Alice confirms the evaluations and the pothole positions. The mobile app will send the data to the server and make them publicly available.
\end{enumerate}

\paragraph{Scenario 2: Manual Insertion and Path Publishing}
\textbf{Actors:} Bob (Registered User), Web App.\\
Bob decides to add a bike path he has just completed to help his local biking community.
\begin{enumerate}
    \item Bob logs on the website.
    \item He selects "Add new path" and uses the interface to select the starting point and the destination point.
    \item Bob add also a few obsacles he encountered during in his path and marks the path's status at "Good".
    \item He selects also to make public those informations.
    \item The system save the data Bob sent and make them available to other users and non-users.
\end{enumerate}

\paragraph{Scenario 3: Search and Path Visualization}
\textbf{Actors:} Charlie (Non registered user), Web App.\\
Charlie needs to quickly see which is the optimal (meaning shortest and with better road quality and fewer obstacles) bike path to reach a destination.
\begin{enumerate}
    \item Charlie visits the BBP's website senza without logging in.
    \item Through the UI he inserts the origin (his position) and the destination.
    \item The system will elaborate and will find a list of possible paths.
    \item Two paths are considered the optimals. Path A is the shortest but is marked with status "Fair". Path B is longer but is marked with status "Very Good".
    \item The system will choose path B, basing his choice on the better road quality.
    \item Charlie selects Path B and it will open it on his device's map's app.
\end{enumerate}
\subsubsection{Use Case Scenarios}

\subsubsection{Domain Model}

\subsection{Product Functions}

\subsection{User Characteristics}

\subsection{Assumptions, Dependencies, and Constraints}